For the second part of the lab, we are to assume that we have a system with
three independent variables: A, B, C. Each variable has three posisble values:
0, 1, 2. There is no actual testing for this portion, it is a conceptual
exercise.

In total, there are $3 \times 3 \times 3  = 27$ test cases if we were to do
combinatorial testing. We are looking for a standard orthogonal array that
can fit $3^3$. From \url{http://neilsloane.com/oadir/}, we find that
the $L_9(3^4)$ standard orthogonal array works. 
Below is the set of test cases using the orthogonal array mentioned above:

\inputminted{text}{resources/standard3^4}

The PICT program (\url{https://github.com/microsoft/pict}) was used to generate
test cases with the following input:

\inputminted{text}{resources/pict}

It should be noted that strangely, there seems to be different outputs
depending on the operating system that pict is run on.

On GNU/Linux systems, the output is as follows:
\inputminted{text}{resources/pictlinux}

On Windows, the output is as follows:
\inputminted{text}{resources/pictwindoze}

On MacOS, the output is as follows:
\inputminted{text}{resources/pictmacos}

What is strange is that on the Windows and MacOS systems, 10 test cases are
generated, while on GNU/Linux, 11 test cases are generated. 

Given the inconsistent outputs of the pict tool depending on the operating
system that the program is run on, I am not sure about the effectiveness of the
tool for test case generation. Ideally, the test cases generated should be
consistent, since this they are not supposed to be chosen randomly. If the
program worked consistently, however, it would be quite effective since not
much effort would be required to come up with the test cases, and we have the
guarantee that every pair of inputs is tested. 

Compared to the orthogonal array, the pict tool generated more test cases


Pairwise testing is fairly useful, especially when you consider it versus
combinatorial testing. In this toy example, the number of test cases was not
reduced that much, (27 for combinatorial testing, versus 9 with an orthogonal
table), but one can imagine the reduction in test cases when there are more
inputs, and more possible values that these inputs can take on. Compared with
random combinations, pairwise testing gives us the guarantee that we are
testing every single pair of input factors, whereas random combinations
does not have this guarantee, and there are far more combinations to choose
from. However, random combinations can by chance reveal errors that pairwise
testing would not catch.
